---
output:
  html_document: default
  html_notebook: default
  pdf_document: default
  word_document: default
---

# ASSIGNMENT
### By Jerry John 

# Different ways to generate random numbers in R

## Uniform numbers

To generate random numbers from a uniform distribution you can use the runif() function. Alternatively, you can use sample() to take a random sample using with or without replacements.


```{r}
n =10
# generate n random numbers between the default values of 0 and 1
runif(n)            

```

```{r}

# generate n random numbers between 0 and 25
runif(n, min = 0, max = 25)       

 
```

```{r}
# generate n random numbers between 0 and 25 (with replacement)
sample(0:25, n, replace = TRUE)
```


```{r}
# generate n random numbers between 0 and 25 (without replacement)
sample(0:25, n, replace = FALSE) 
```

## Normal Distribution Numbers

The normal (or Gaussian) distribution is the most common and well know distribution.

```{r}
# generate n random numbers from a normal distribution with given mean & st. dev.
rnorm(n, mean = 0, sd = 1) 
```

## Binomial Distribution Numbers


This is conventionally interpreted as the number of successes in size = x trials and with prob = p probability of success:

```{r}
# generate a vector of length n displaying the number of successes from a trial 
# size = 100 with a probabilty of success = 0.5
rbinom(n, size = 100, prob = 0.5) 
```

## Poisson Distribution Numbers

The Poisson distribution is a discrete probability distribution that expresses the probability of a given number of events occuring in a fixed interval of time and/or space if these events occur with a known average rate and independently of the time since the last event.


```{r}
# generate a vector of length n displaying the random number of events occuring 
# when lambda (mean rate) equals 4.
rpois(n, lambda = 4) 
```

## Exponential Distribution Numbers

The Exponential probability distribution describes the time between events in a Poisson process.

```{r}
# generate a vector of length n with rate = 1
rexp(n, rate = 1)  
```

## Gamma Distribution Numbers

The Gamma probability distribution is related to the Beta distribution and arises naturally in processes for which the waiting times between Poisson distributed events are relevant.

```{r}
# generate a vector of length n with shape parameter = 1
rgamma(n, shape = 1)
```
























































